MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-11-13 article/main.tex
Ethereum section added to background

\title{MixEth: efficient trustless coin mixing service for Ethereum}
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

\textbf{Note: this is an early-stage work-in-progress! Security proofs, (state channel) implementation and many more are yet to come!} 
\begin{abstract}
Cryptocurrencies enable users to transact with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to this transparent nature of the ledger, privacy is notably reduced. If the link between users' public key and their physical identity is exposed  their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only $3$ on-chain transactions at most per user and $1$ off-chain. It achieves strong notions of anonymity and is able to resist denial-of-service attacks.      
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer}

@@

\textbf{Our contributions.} In this paper, we present MixEth, to overcome the above mentioned efficiency issues while retaining strong notions of anonymity already achieved by previous proposals. MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas. Game-theoretical analysis of incentives in MixEth is also enclosed.

@@

We use games in definitions and proofs of security. At the end of each game, the main procedure of game \textsf{G} outputs a single bit. $\Pr(\textsf{G})$ denotes the probability that the output is $1$.
\subsection{Cryptographic keys in Ethereum}
Ethereum uses Elliptic Curve Cryptography (ECC) to secure users' funds. More specifically, it uses the secp256k1 curve, the same one as used in Bitcoin. If a user wants to create an Ethereum address, first she needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite field $\mathbb{F}_{p}$. The corresponding public key will be $sG$. Note that any multiples of $G$ is also a generator of curve points since $n$, the order of the group is also a prime. Accounts in Ethereum are identified by their addresses which can be obtained by taking the right most 20 bytes of the Keccak hashed public key \cite{wood2014ethereum}.

@@

So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well.

@@

 Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers

@@

>>>>

\title{MixEth: efficient, trustless coin mixing service for Ethereum}
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

\textbf{Note: this is an early-stage work-in-progress! Security proofs, (state channel) implementation and many more are yet to come!} 
\begin{abstract}
Cryptocurrencies enable users to transact with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to the ledger's transparent nature, privacy is notably reduced. If the link between users' public key and their physical identity is exposed, their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only $3$ on-chain transactions at most per user and $1$ off-chain. It achieves strong notions of anonymity and is able to resist denial-of-service attacks.      
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer}

@@

\textbf{Our contributions.} In this paper, we present MixEth, to overcome the above mentioned efficiency issues while retaining strong notions of anonymity already achieved by previous proposals. MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.

@@

We use games in definitions and proofs of security. At the end of each game, the main procedure of game \textsf{G} outputs a single bit. $\Pr(\textsf{G})$ denotes the probability that the output is $1$.
\subsection{Cryptographic keys in Ethereum}
Ethereum uses Elliptic Curve Cryptography (ECC) to secure users' funds. More specifically, it uses the secp256k1 curve, the same one as used in Bitcoin. If a user wants to create an Ethereum address, first they needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite prime field $\mathbb{F}_{p}$. The corresponding public key will be $sG$. Note that any multiples of $G$ is also a generator of curve points since $n$, the order of the group is also a prime. Accounts in Ethereum are identified by their addresses which can be obtained by taking the right most 20 bytes of the Keccak hashed public key \cite{wood2014ethereum}.

@@

So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well. The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succints proofs for the incorrectness of the shuffle, if applies.

@@

 Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers.

@@

Ethereum is a cryptocurrency built on top of a blockchain. Similarly to Bitcoin, network participants broadcast transactions in a peer-to-peer network, where transactions are bundled together into blocks that are appended to a public ledger called blockchain. Only those specific nodes can append new blocks to the blockchain who previously solved a difficult cryptographic puzzle. The state of the system consists of the state of different accounts populating it.

In Ethereum currently there are two types of accounts. The first account type is called \textit{externally owned account}. It owns an ECDSA keypair controlled by its user. Private keys are used to sign transactions. On the other hand there are \textit{contract accounts}, often smart contracts, that additionally have persistent storage and contract's code. Both of the account types have Ether balances, which is the native currency of the Ethereum network. Ether is denominated in wei, where $1\ ETH = 10^ {18}\ wei$.

Transactions can alter the system's state by either creating a contract account or by calling to an existing account. Transactions to externally owned accounts can only transfere Ether, while transactions to contract accounts can additionally execute the code associated with them. Codes are executed in a quasi-Turing complete execution environment, called Ethereum Virtual Machine (EVM).

EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}. In every gas the sender needs to pay upfront for the execution of the contract's code. The computational complexity of a transaction is measured in gas, which can be bought for Ether on a price set by the transaction originator, so called gas price. Therefore the transaction fee is the gas cost multiplied by the gas price. One needs to specify a gas limit, meaning that they do not allow their transaction to burn more gas than the limit. If a transaction during execution runs out of gas, then all the state changes are reverted, while the transaction fee is paid to the miner. If there are gas left after successful execution, transaction originator is reimbursed. Additionally there exists a block gas limit, which limits the number of computational steps fitting in one block. Currently the block gas limit is cca. $\num[group-separator={,}]{8000000}$ gas. Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as less as possible on transactions fees. Small gas costs are also crucial from a scalability point of view, since the less gas burnt for each transaction, the more transaction can fit into a single block.
